An Open Platform for Managing Short Programming Exercises

### 2013-06-19 paper/paper.tex
more discussion questions

@@

{\bf Can exercises be reused effectively outside of the course in which
they were originally created?}  When assigning a programming exercise to
students, the instructor can create one from scratch, or use a
previously-written exercise.  Since creating good exercises is labor-intensive,
being able to use a previously-written exercise represents a significant
time savings.  However, finding an existing exercise that is {\em appropriate}
is not necessarily a trivial task.  We are interested in finding
out whether exercises written in the context of one course can be reused
effectively in another.

>>>>

\newenvironment{denseItemize}{%
\begin{list}{$\bullet$}{\setlength{\itemsep}{0in}\setlength{\parsep}{0in}\leftmargin=1em\labelwidth=1em}}{\end{list}}

@@

{\bf Can exercises be reused effectively outside of the course in which
they were originally created?}  When assigning a programming exercise to
students, the instructor can create one from scratch, or use a
previously-written exercise.  Since creating good exercises is labor-intensive,
being able to use a previously-written exercise represents a significant
time savings.  However, finding an existing exercise that is {\em appropriate}
is not necessarily a trivial task.  We are interested in finding
out whether exercises written in the context of one course can be reused
effectively in another.  There are many interesting aspects of
this question:

\begin{denseItemize}
\item How can we help instructors search for appropriate exercises?
\item How can we classify exercises?
\item Can we allow CloudCoder users to {\em improve} existing exercises?
\end{denseItemize}

{\bf What guidance can we provide to instructors on which exercises to assign,
and in what order?}  This question is an expanded form of the previous question:
if a large repository of pre-written exercises is available,
could we offer instructors sequences of exercises on a particular topic?

{\bf How can programming exercises be integrated most effectively into a course?}
Programming exercises can be used for many purposes: self-test questions
to accompany readings and video lectures, in-class assessment (possibly
in the context of peer instruction), extra practice for students who
are struggling.  We would like to have specific, evidence-based recommendations
that we can give to instructors who are considering using programming
exercises in their courses.
